Randomized Algorithms \\ Assignment 1

### 2017-04-30 assignments/1/paper.tex
Started typing in 1.2

\section*{Exercise 1.2}
Consider the graph $G=(E,V)$ consisting of two $(\left|V\right|/2)$-cliques, $L$ and $R$, connected by a single edge. The min-cut of $G$ has size 1. If at any point, the algorithm coalesces any pair of vertices that are not both from $L$ or $R$, respectively, the size of the min-cut increases in the resulting graph, and it can not be found in subsequent iterations.

@@

\paragraph{b)} The claim is correct, since there is a 0 probability of a collisions occurring if the numbers are picked from the interval, uniformly, at random. However an unbounded number of bits are required to represent such a number, and hence a lazy approach, such as the one described in c) is required.

>>>>

\section*{Exercise 1.2}
Consider the graph $G=(V,E)$ consisting of two $(\left|V\right|/2)$-cliques, $L$ and $R$, connected by a single edge (assume that $|V|$ is even, without loss of generality). The min-cut of $G$ has size 1. If at any point, the algorithm coalesces any pair of vertices that are not both from $L$ or $R$, respectively, the size of the min-cut increases in the resulting graph, and it can not be found in subsequent iterations. Let $\varepsilon$ denote the event that a pair of vertices from either clique are chosen. Then 
\begin{align*}
\mathbf{Pr}\left[ \varepsilon \right] = \frac{\binom{|L|}{2} + \binom{|R|}{2}}{\binom{|L|+|R|}{2}}
\end{align*}

@@

\paragraph{b)} The claim is correct, since there is a 0 probability of collisions occurring if the numbers are picked from the interval, uniformly, at random. However an unbounded number of bits are required to represent such a number, and hence a lazy approach, such as the one described in c) is required.
